Plant-pollintor networks worldwide are composed by the same specific building blocks

### 2021-05-18 Draft/Draft.Rmd
Update Draft.Rmd

#Fig 1 Should be a dot plot (or forest plot) of the mean +- SE of the 15 motifs.
```
2) FG-position associations.
```{r}
library(lme4)
library(tidyverse)
source("../Scripts/Scripts_Alfonso/add_study_id.R")

@@

@@

plant_position_percentiles_filtered <- all_position_percentiles %>% 
  filter(Node_FG %in% list_plants_FG, !position %in% c("np1","np2"),
         !is.na(expected_freq_its_GF))
pollinator_position_percentiles_filtered <- all_position_percentiles %>% 
  filter(!Node_FG %in% list_plants_FG, !position %in% c("np1","np2"),
         !is.na(expected_freq_its_GF))

>>>>

#Fig 1 Should be a dot plot (or forest plot) of the mean +- SE of the 15 motifs.
```
2) FG-position associations.
```{r}
library(lme4)
library(tidyverse)
library(stringi)
source("../Scripts/Scripts_Alfonso/add_study_id.R")

@@

all_position_percentiles$position <- stri_extract_first_regex(all_position_percentiles$position,
                                                              "[0-9]+") %>% as.numeric()

@@

plant_position_percentiles_filtered <- all_position_percentiles %>% 
  filter(Node_FG %in% list_plants_FG, !position %in% c(1,2),
         !is.na(expected_freq_its_GF))
pollinator_position_percentiles_filtered <- all_position_percentiles %>% 
  filter(!Node_FG %in% list_plants_FG, !position %in% c(1,2),
         !is.na(expected_freq_its_GF))
